### 2016-08-28 paper.tex
Add definitions for symbols near where they're first used

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow hydrokinetic
(river) turbine that was designed to operate in a reach of the lower Mississippi
River near Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has
three tapered blades and a relatively low solidity $Nc/(\pi D)$ or
chord-to-radius ratio $c/R \approx 0.1$. A preliminary analysis with Sandia's
CACTUS vortex line numerical model \cite{Murray2011} predicted an individual
rotor's full-scale performance coefficient to be $C_P=0.47$ at 1 m/s flow speed
and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} = 3.15$
\cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity and
radius, respectively. Note that the RM2 rotor solidity would be considered
moderate to high for a wind turbine, whose $c/R$ values typically range from
0.05 to 0.09, but MHK rotors are typically higher solidity since they must
withstand approximately an order of magnitude higher torque in typical flows,
necessitating relatively larger blades to meet strength and fatigue life
requirements.

>>>>

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow hydrokinetic
(river) turbine that was designed to operate in a reach of the lower Mississippi
River near Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has
three tapered blades and a relatively low solidity $Nc/(\pi D)$, where $N$ is
the number of blades, $c$ is the chord length, and $D$ is the rotor diameter, or
chord-to-radius ratio $c/R \approx 0.1$. A preliminary analysis with Sandia's
CACTUS vortex line numerical model \cite{Murray2011} predicted an individual
rotor's full-scale performance coefficient to be $C_P \equiv P / \left(
\frac{1}{2} \rho A U_\infty^3 \right) = 0.47$---where $P$ is the mechanical
power output, $\rho$ is the fluid density, $A$ is the rotor frontal area, and
$U_\infty$ is the free stream velocity---at 1 m/s flow speed and a tip speed
ratio $\lambda \equiv \frac{\omega R}{U_\infty} = 3.15$ \cite{Barone2011}, where
$\omega$ and $R$ are the rotor's angular velocity and radius, respectively. Note
that the RM2 rotor solidity would be considered moderate to high for a wind
turbine, whose $c/R$ values typically range from 0.05 to 0.09, but MHK rotors
are typically higher solidity since they must withstand approximately an order
of magnitude higher torque in typical flows, necessitating relatively larger
blades to meet strength and fatigue life requirements.
